---
title: Projects
toc: true
toc-title: ""
toc-location: left
---

```{r}
#| label: fn
#| echo: false
enlink_fa <- function(link, fa) {
  if (link == "") return(" ")
  paste0("[", fontawesome::fa(fa), "](", link, ")")
}
```

Almost everything listed on this page was built for the sake of my own learning. Quality and completeness are variable. No guarantees.

## R Packages

Selected packages. All are hosted on GitHub. Many are [on my R-universe](https://matt-dray.r-universe.dev/). 

### Useful

Made to serve a 'real' purpose. Other people could feasibly find them useful. Nothing grandiose. Alphabetical.

```{r}
#| label: packages-useful
#| echo: false

pkgs <- read.csv("resources/packages.csv")

pkgs$Links <- paste(
  lapply(pkgs$source_url, \(x) enlink_fa(x, "github")),
  lapply(pkgs$blog_url,   \(x) enlink_fa(x, "pencil"))
)

pkgs$Name <- paste0("{", pkgs$Name, "}")

pkgs[
  pkgs$category == "Useful",
  c("Name", "Description", "Links")
] |> 
  knitr::kable(row.names = FALSE)
```

### Conceptual

Experiments, games, hacks, memes and subversion. Alphabetical.

```{r}
#| label: packages-concept
#| echo: false
pkgs[
  pkgs$category == "Concept",
  c("Name", "Description", "Links")
] |> 
  knitr::kable(row.names = FALSE)
```

## Shiny apps

### Hosted 

<img src='https://img.shields.io/badge/Shiny-shinyapps.io-447099?style=flat&labelColor=white&logo=Posit&logoColor=447099'>

```{r}
#| label: shiny-shinyapps
#| echo: false
tibble::tribble(
  ~Name, ~Description, ~Links,
  # 
  "Animal Crossing Popularity Contest", 
  "Swipe left or right on villagers from Nintendo’s Animal Crossing",
  paste(
    enlink_fa("https://mattdray.shinyapps.io/acnh-swipe/", "globe"),
    enlink_fa("https://github.com/matt-dray/acnh-swipe", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2022-01-07-acnh-swipe-results/", "pencil")
  ),
  # 
  "LeWitt ReMix", 
  "Remix Sol LeWitt's art for #RecreationThursday",
  paste(
    enlink_fa("https://mattdray.shinyapps.io/lewitt-remix-app/", "globe"),
    enlink_fa("https://github.com/matt-dray/viz-recreation/tree/main/2021-07-01_rt_lewitt/lewitt-remix-app/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2021-07-05-recreate-lewitt/", "pencil")
  ),
  # 
  "Randoflag", 
  "A randomised flag challenge for new browser tabs",
  paste(
    enlink_fa("https://mattdray.shinyapps.io/randoflag/", "globe"),
    enlink_fa("https://github.com/matt-dray/randoflag/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2021-03-02-randoflag/", "pencil")
  ),
  #
  "What’s your Hadley number?", 
  "Find shortest paths to Hadley Wickham in the CRAN authorship graph",
  paste(
    enlink_fa("https://mattdray.shinyapps.io/hadley-number/", "globe"),
    enlink_fa("https://github.com/matt-dray/hadley-number/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2019-02-27-hadley-number/", "pencil")
  )
) |> 
  knitr::kable()
```

### Shinylive

<img src='https://img.shields.io/badge/Shiny-shinylive-447099?style=flat&labelColor=white&logo=Posit&logoColor=447099'>

Serverless. Runs entirely in your browser.

```{r}
#| label: shiny-shinylive
#| echo: false
tibble::tribble(
  ~Name, ~Description, ~Links,
  # 
  "CRAN deadlines", 
  "See which CRAN packages are at threat of archival",
  paste(
    enlink_fa("https://matt-dray.github.io/cran-deadlines/", "globe"),
    enlink_fa("https://github.com/matt-dray/cran-deadlines/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2024-06-12-cran-db/", "pencil")
  ),
  # 
  "Govspeakify tables", 
  "Convert a pasted table to Govspeak-flavoured Markdown",
  paste(
    enlink_fa("https://matt-dray.github.io/govspeakify-tables/", "globe"),
    enlink_fa("https://github.com/matt-dray/govspeakify-tables/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2023-10-08-govspeakify-tables/", "pencil")
  ),
  #
  "Little pixel fun zone", 
  "A small interactive pixel-editor toy for the browser",
  paste(
    enlink_fa("https://matt-dray.github.io/little-pixel-fun-zone/", "globe"),
    enlink_fa("https://github.com/matt-dray/little-pixel-fun-zone/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2024-09-15-shiny-pixel/", "pencil")
  ),
  # 
  "Not Balatro", 
  "Drag-and-drop card gaming in R with {sortable}?",
  paste(
    enlink_fa("https://matt-dray.github.io/not-balatro/", "globe"),
    enlink_fa("https://github.com/matt-dray/not-balatro/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2024-10-25-not-balatro/", "pencil")
  ),
) |> 
  knitr::kable()
```

### Not hosted

<img src='https://img.shields.io/badge/Shiny-not_hosted-447099?style=flat&labelColor=white&logo=Posit&logoColor=447099'>

You'll have to download and run them yourself.

```{r}
#| label: shiny-not-hosted
#| echo: false
tibble::tribble(
  ~Name, ~Description, ~Links,
  # 
  "Ages at World Cup 2018", 
  "You're really old and sports people are younger than you",
  paste(
    enlink_fa("https://github.com/matt-dray/wc18-age/", "github"),
    enlink_fa("https://www.rostrum.blog/2018/07/17/world-cup-age-app/", "pencil")
  ),
  # 
  "Deer-vehicle collisions in Scotland", 
  "Explore open data on deer strikes in Scotland, 2000 to 2017",
  paste(
    enlink_fa("https://github.com/matt-dray/scot-deer-collisions/", "github"),
    enlink_fa("https://www.rostrum.blog/2019/01/18/deer-collisions/", "pencil")
  ),
  # 
  "Mission Across IOW", 
  "How hard is it to cross the Isle of Wight, UK, in a straight line?",
  paste(
    enlink_fa("https://github.com/matt-dray/mission-across-iow/", "github"),
    enlink_fa("https://www.rostrum.blog/2021/05/22/mission-across-iow/", "pencil")
  ),
  # 
  "Read a colour hex code", 
  "Test yourself at reading colour hex codes by eye ",
  paste(
    enlink_fa("https://github.com/matt-dray/dehex-challenge/", "github"),
    enlink_fa("https://www.rostrum.blog/2021/08/10/dehex/", "pencil")
  ),
  # 
  "Tidyquiz", 
  "A {learnr} hack to generate a random {tidyverse} functions quiz",
  paste(
    enlink_fa("https://github.com/matt-dray/tidyquiz/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2019-03-18-tidyverse-quiz/", "pencil")
  ),
) |> 
  knitr::kable()
```

## Websites

```{r}
#| label: websites
#| echo: false
tibble::tribble(
  ~Name, ~Description, ~Tools, ~Links,
  # 
  "matt-dray.com", 
  "This website",
  "Quarto, Netlify",
  paste(
    enlink_fa("https://www.matt-dray.com/", "globe"),
    enlink_fa("https://www.github.com/matt-dray/personal-site/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2020-12-08-postcard/", "pencil")
  ),
  #
  "rostrum.blog", 
  "Japes with R: tutorials, ephemera, memes",
  "Quarto, Netlify",
  paste(
    enlink_fa("https://www.rostrum.blog/", "globe"),
    enlink_fa("https://www.github.com/matt-dray/rostrum-blog-2/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2023-08-26-cheerio-blogdown/", "pencil")
  ),
  #
  "faxcrayon.art", 
  "A gallery of recreations/remixes/original art",
  "RMarkdown, {bs4cards}, GitHub Pages",
  paste(
    enlink_fa("https://www.faxcrayon.art/", "globe"),
    enlink_fa("https://www.github.com/matt-dray/faxcrayon/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2021-07-25-faxcrayon/", "pencil")
  ),
  #
  "Hastings Half maps", 
  "Interactive maps of the Hastings Half-Marathon route",
  "RMarkdown, {flexdashboard}, GitHub Pages",
  paste(
    enlink_fa("https://matt-dray.github.io/hastings-half/", "globe"),
    enlink_fa("https://github.com/matt-dray/hastings-half/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2022-03-31-hastings-half/", "pencil")
  )
) |> 
  knitr::kable()
```

## Other

Code-based bric-a-brac. Alphabetical.

```{r}
#| label: other
#| echo: false
tibble::tribble(
  ~Name, ~Description, ~Links,
  # 
  "Emojis to SVG", 
  "Script to fetch SoftBank’s 1997 emoji set (the first-ever?) and convert them to SVG format",
  paste(
    enlink_fa("https://github.com/matt-dray/og-emoji-svg/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2021-07-31-og-emoji-svg/", "pencil")
  ),
  # 
  "gamelad", 
  "An RStudio theme to mimic the original GameBoy’s green palette",
  paste(
    enlink_fa("https://github.com/matt-dray/gamelad/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2021-01-04-safar6/", "pencil")
  ),
  # 
  "GitHub Gists", 
  "Snippets of code that solve a small problem and sometimes become blog posts",
  enlink_fa("https://gist.github.com/matt-dray/", "github"),
  # 
  "Hex stickers", 
  "Hexagonal sticker designs, mostly for R packages",
  enlink_fa("https://github.com/matt-dray/stickers/", "github"),
  # 
  "londonmapbot", 
  "A (retired) social media bot that posts MapBox satellite images, made with {rtoot} and GitHub Actions",
  paste(
    enlink_fa("https://botsin.space/@londonmapbot", "mastodon"),
    enlink_fa("https://twitter.com/londonmapbot", "twitter"),
    enlink_fa("https://github.com/matt-dray/londonmapbot/", "github"),
    enlink_fa("https://www.rostrum.blog/index.html#category=londonmapbot/", "pencil")
  ),
  # 
  "Splendid R games", 
  "A list of games made with R",
  paste(
    enlink_fa("https://github.com/matt-dray/splendid-r-games/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2023-04-02-splendid-r-games/", "pencil")
  ),
  # 
  "Tidyswirl", 
  "A work-in-progress introduction to the tidyverse created with {swirl}",
  paste(
    enlink_fa("https://github.com/matt-dray/tidyswirl/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2019-11-02-tidyswirl/", "pencil")
  ),
  # 
  "Try R v4.2", 
  "Try new features of R version 4.2 in the browser, thanks to Binder",
  paste(
    enlink_fa("https://mybinder.org/v2/gh/matt-dray/try-Rv4.2/main?urlpath=rstudio/", "globe"),
    enlink_fa("https://github.com/matt-dray/try-Rv4.2/", "github"),
    enlink_fa("https://www.rostrum.blog/posts/2022-06-01-try-r/", "pencil")
  ),
) |> 
  knitr::kable()
```
